A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/main_RECOMB.tex
added raw equations to recomb
improved and clean dataset construction (clustering requires cd-hit)
Reorganized method section
new title
intro
new roc figs
Dynamic programming Figures
New title + removed todo
fixed intro (abstract missing)
added abstract

\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in,right=1in,left=1in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm} %pour les newtheorem
\usepackage{epstopdf}
\usepackage{xspace}
\usepackage[numbers]{natbib}

\usepackage{subfig} %Subfigures

@@

\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\farna}{\texttt{FARNA}\xspace}
\newcommand{\mcfoldmcsym}{\texttt{MC-Pipeline}\xspace}
\newcommand{\mcfold}{\texttt{MC-Fold}\xspace}
\newcommand{\mcsym}{\texttt{MC-Sym}\xspace}
\newcommand{\nast}{\texttt{NAST}\xspace}
\newcommand{\ifoldrna}{\texttt{iFoldRNA}\xspace}
\newcommand{\rnafold}{\texttt{RNAfold}\xspace}
\newcommand{\rnasubopt}{\texttt{RNAsubopt}\xspace}
\newcommand{\rnawolf}{\texttt{RNAwolf}\xspace}
\newcommand{\rnastructure}{\texttt{RNAstructure}\xspace}
\newcommand{\contrafold}{\texttt{contrafold}\xspace}
\newcommand{\unafold}{\texttt{unafold}\xspace}
\newcommand{\rnadd}{\texttt{RNA2D3D}\xspace}
\newcommand{\assemble}{\texttt{assemble}\xspace}
\newcommand{\fred}{\texttt{FR3D}\xspace}
\newcommand{\rnajunction}{\texttt{RNAjunction}\xspace}
\newcommand{\rnamotif}{\texttt{RNAmotif}\xspace}
\newcommand{\treefolder}{\texttt{TreeFolder}\xspace}
\newcommand{\barnacle}{\texttt{BARNACLE}\xspace}
\newcommand{\contextfold}{\texttt{contextfold}\xspace}
%\newcommand{\citep}{\cite}

\title{RNApyro}
\author{}
\date{}

@@

\begin{document}
\maketitle
%\section{}
%\subsection{}
\begin{abstract}
Some stuff~\cite{Waldispuhl2008}

\noindent
\textbf{Key words:} RNA
\end{abstract}

>>>>

\documentclass[11pt]{article}
\usepackage[top=1in, bottom=1in,right=1in,left=1in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm} %pour les newtheorem
\usepackage{epstopdf}
\usepackage{xspace}
\usepackage{relsize}
\usepackage[numbers]{natbib}
\usepackage[colorinlistoftodos]{todonotes}

%\usepackage{subfig} %Subfigures
\usepackage{subcaption} %Subfigures

\usepackage{tikz}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{relsize}
\usetikzlibrary{positioning}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{fit}
\usetikzlibrary{decorations}
\usetikzlibrary{snakes}
\pgfdeclarelayer{background}
\pgfdeclarelayer{backbackground}
\pgfdeclarelayer{foreground}
\pgfsetlayers{backbackground,background,main,foreground}

@@

\newcommand{\RNAmutants}{\texttt{RNAmutants}\xspace}
\newcommand{\RNApyro}{\texttt{RNApyro}\xspace}

\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\farna}{\texttt{FARNA}\xspace}
\newcommand{\mcfoldmcsym}{\texttt{MC-Pipeline}\xspace}
\newcommand{\mcfold}{\texttt{MC-Fold}\xspace}
\newcommand{\mcsym}{\texttt{MC-Sym}\xspace}
\newcommand{\nast}{\texttt{NAST}\xspace}
\newcommand{\ifoldrna}{\texttt{iFoldRNA}\xspace}
\newcommand{\rnafold}{\texttt{RNAfold}\xspace}
\newcommand{\rnasubopt}{\texttt{RNAsubopt}\xspace}
\newcommand{\rnawolf}{\texttt{RNAwolf}\xspace}
\newcommand{\rnastructure}{\texttt{RNAstructure}\xspace}
\newcommand{\contrafold}{\texttt{contrafold}\xspace}
\newcommand{\unafold}{\texttt{unafold}\xspace}
\newcommand{\rnadd}{\texttt{RNA2D3D}\xspace}
\newcommand{\assemble}{\texttt{assemble}\xspace}
\newcommand{\fred}{\texttt{FR3D}\xspace}
\newcommand{\rnajunction}{\texttt{RNAjunction}\xspace}
\newcommand{\rnamotif}{\texttt{RNAmotif}\xspace}
\newcommand{\treefolder}{\texttt{TreeFolder}\xspace}
\newcommand{\barnacle}{\texttt{BARNACLE}\xspace}
\newcommand{\contextfold}{\texttt{contextfold}\xspace}
%\newcommand{\citep}{\cite}
\newcommand{\Z}[3]{\mathcal{Z}_{\substack{(#1)\\ [#3]}}^{#2}}
\newcommand{\Y}[3]{\mathcal{Y}_{\substack{(#1)\\ [#3]}}^{#2}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\Kron}{\delta}
\newcommand{\ub}{\bullet}

%\title{An inside-outside algorithms for mutant RNAs with applications to error detections in structured RNAs}
\title{A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences}
\author{Vladimir Reinharz, Yann Ponty$^{*}$, J\'er\^{o}me Waldisp\"{u}hl$^*$}
\date{}

@@

\begin{document}
\maketitle
%\section{}
%\subsection{}
\begin{abstract}
Analysis of the sequence-structure relationship in RNA molecules are essential to evolutionary studies but also to 
concrete applications such as error-correction methodologies in sequencing technologies. The prohibitive sizes of the
mutational and conformational landscapes combined with the volume of data to proceed require efficient algorithms 
to compute sequence-structure properties. More specifically, here we aim to calculate which mutations increase the most the 
likelihood of a sequence to a given structure and RNA family.\\
In this paper, we introduce \RNApyro, an efficient linear-time and space inside-outside algorithm that computes exact mutational
probabilities under secondary structure and evolutionary constraints given as a multiple sequence alignment with a consensus structure.
We develop a scoring scheme combining classical stacking base pair energies to novel isostericity scales, and apply our techniques
to correct point-wise errors in 5s rRNA sequences. Our results suggest that \RNApyro is a promising algorithm to complement existing
tools in the NGS error-correction pipeline.

\noindent
\textbf{Key words:} RNA, mutations, secondary structure
\end{abstract}
